The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-17 paper.tex
Adding in comments from recent kmos3d splash of papers

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift Universe.
We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
\end{abstract}

@@

Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017}.
In both cases, systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.

@@

Our data for the 77 KDS targets were observed using KMOS.
KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RGHgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band filter has spectral resolution of $R \sim 4200$.
\subsubsection{Observations}\label{subsubsec:Obs}
To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously. \\

@@

\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
In Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.

@@

\subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe:

@@

In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
These galaxies are representative of typical SFGs $z\sim3.5$ as verified by comparing to fits to the galaxy main sequence at this redshift.
Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e. not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}. \\

Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample', placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{app:comparison_samples}.
In \cref{app:comparison_samples} we describe also the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.  \\

@@

In the $\Lambda CDM$ paradigm, galaxies form when baryons accumulate and cool in the centres of dark matter halos, subsequently forming a rotating disk of stars and gas.
The relationship between stellar mass and rotation velocity describes the connection between the luminous mass and the total dynamical mass in a system.
The connection has been studied extensively at low redshift \citep[e.g.][]{Bell2000a,Rhee2003,Reyes2011} with fits to late-type, rotating galaxies in the $V_{C}-M_{\star}$ plane having a well-defined slope and normalisation.
Observing this `stellar mass Tully-Fisher relation' at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies \citep[e.g.][]{Dubois2014a,Vogelsberger2014b,Schaye2015}.
In principle, studying whether the stellar mass Tully-Fisher relation evolves with redshift gives us information about when galaxies accumulate their stellar mass and rotation velocities.
Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Swinbank2012,Straatman2017}. \\

The main question arising from observations in support of and against evolution of the stellar mass Tully-Fisher relation with redshift is: Do galaxies evolve along a relation which is fixed or is there a shift in the zero-point and/or slope with decreasing redshift (i.e. is the connection between $V_{C}$ and the accumulating $M_{\star}$ fixed at all times)?
We'd like to know how an individual, unperturbed point, representing a typical rotation-dominated SFG allowed to evolve without mergers, would move around the $V_{C}$ vs. $M_{\star}$ plane over 12 Gyr of purely secular evolution.

Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017}.
However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,Pelliccia2016,DiTeodoro2016,Simons2016,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of -1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation. \\

@@

With the inclusion of the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\sim0.1$ and $z\sim3.5$.
However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.

@@

In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field sample to highlight two observations:
\begin{itemize}
    \item At each redshift slice the $V_{C}$ distributions are extremely broad.
    \item The mean isolated field sample $V_{C}$ value is less than reported in the comparison samples with similar mean $M_{\star}$ values.
    This is a result of averaging over a sample containing a higher fraction of dispersion dominated galaxies.
\end{itemize}

@@

The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.

We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
Further than this, there are some galaxies where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g. see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
This suggests that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Tacconi2013,Wisnioski2015}.
These ideas are explored in the following sections.

@@

In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs. $M_{\star}$ plane.
This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Kassin2012}.
However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Wisnioski2015}, leaving $\sigma_{int}$ as a challenging property to interpret. \\

@@

In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
Using observed constraints for these properties \citep{Tacconi2013,Tacconi2017} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
The relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.  \\

>>>>

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift Universe.
We have made careful comparisons to other samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The mean dispersion value of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\sim3$ in other samples.
However only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
These random motions are likely to provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

Recent cosmological volume simulations are able to resolve the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014a,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between dark matter halos and the baryons and the dissipation of this angular momentum thereafter (through gravitational collpase, mergers and outflows \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulators to attempt to match.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017} and when interpreted in tandem with high-resolution imaging data from the Hubble Space Telescope ({\em {\em HST}}) these data provide exquisite information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to build up over much shorter timescales \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2016,Harrison2017} providing an order of magnitude boost in statistical power over previous high-redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016a,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in the last few years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk result in a decrease in the observed rotational velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

@@

Our data for the 77 KDS targets were observed using KMOS.
KMOS is a second generation IFS mounted at Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the K-band grating has spectral resolution of $R \sim 4200$ (H-band $R \sim 4000$).
\subsubsection{Observations}\label{subsubsec:Obs}
To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the K-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the H-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the H and K-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS HK filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the H-band and K-band regions simultaneously. \\

@@

\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
A Chabrier IMF is used with a reduced set of BC03 \citep{Bruzual2003} templates in the fitting procedure.
We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
In Figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.

@@

\subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
For each galaxy with spatially resolved [O~{\sc III}]$\lambda$5007 emission we construct a series of model datacubes with the same spatial dimensions as the observed datacube and populate each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
This central wavelength is then shifted using the velocity derived at each spaxel from the velocity field model described below.  
Following the procedure now of numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas is modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by equation \ref{eq:arctangent}, which has been found to well match the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:

@@

In the previous sections we have presented our morphological and kinematic analysis for the 77 galaxies covering both cluster and field environments in the KDS survey.
These galaxies are representative of typical SFGs $z\sim3.5$ as verified by comparing to fits to the galaxy main sequence at this redshift.
Through a combined morpho-kinematic classification described in \cref{subsec:morpho-kin-class} we reduce the sample to 32 field galaxies which have spatially resolved [O~{\sc III}]$\lambda$5007 emission and are morphologically isolated (i.e. not merger candidates), which is the largest sample of galaxies observed with integral-field spectroscopy at this redshift.
For these galaxies we have measured morphological properties as listed in Table \ref{tab:phys-props} and extracted intrinsic, beam-smearing corrected measurements of the rotation velocities, $V_{C}$ and velocity dispersions $\sigma_{int}$ as listed in Table \ref{tab:kin_props}, which we use to classify the galaxies as either rotation or dispersion dominated.
The morphological and kinematic grids for these 32 galaxies and the merger candidates are plotted in \cref{app:kinematics_plots}.

Throughout the following sections we analyse the derived kinematic parameters for these 32 galaxies, referred to as the `isolated field sample', placing them in the context of galaxy evolution using the comparison samples spanning a wide redshift baseline described in \cref{app:comparison_samples}.
In \cref{app:comparison_samples} we describe also the variety of methodologies used by the different comparison samples to compute $V_{C}$ and $\sigma_{int}$ as an attempt to help disentangle true evolution in these quantities from offsets originating in disparate measurement techniques.
During the following sections we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that they trace the average properties of typical star-forming galaxies at their respective mean redshifts.

@@

In the $\Lambda CDM$ paradigm, galaxies form when baryons accumulate and cool in the centres of dark matter halos, subsequently forming a rotating disk of stars and gas.
The relationship between stellar mass and rotation velocity describes the connection between the luminous mass and the total dynamical mass in a system.
The connection has been studied extensively at low redshift \citep[e.g.][]{Bell2000a,Rhee2003,Reyes2011} with fits to late-type, rotating galaxies in the $V_{C}-M_{\star}$ plane having a well-defined slope and normalisation.
Observing this `stellar mass Tully-Fisher relation' at different epochs thus offers constraints for galaxy formation and evolution models seeking to explain simultaneously the properties of dark matter halos and the dynamical properties of disk galaxies \citep[e.g.][]{Dubois2014a,Vogelsberger2014b,Schaye2015}.
In principle, studying whether the stellar mass Tully-Fisher relation evolves with redshift gives us information about when galaxies accumulate their stellar mass and rotation velocities.
Any offset from the local relation towards lower $M_{\star}$ values at fixed rotation velocity suggests that the dynamical mass is in place, but the stellar mass is yet to be formed \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Gnerucci2011,Swinbank2012,Straatman2017,Ubler2017}.
As has been discussed recently, information about the redshift evolution of gas fractions, $f_{g} = M_{gas}/M_{bar}$ where $M_{bar}$ is the baryonic mass, disk mass fractions, $m_{d} = M_{bar}/M_{H}$  where $M_{H}$ is the halo mass, dark matter fractions, $f_{DM}(R_{1/2}) = V^{2}_{DM}(R_{1/2})/V^{2}_{C}(R_{1/2})$ where $V_{DM}$ is the dark matter circular velocity, may also be encoded in measured offsets from the local stellar mass Tully-Fisher relation \citep{Wuyts2016b,Ubler2017,Genzel2017}.  \\

Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
High redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
However most find that when selecting rotation dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,Molina2016,DiTeodoro2016,Simons2016,Pelliccia2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
At $z\sim 3$ observations are limited and in \cite{Gnerucci2011} an offset of -1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, with the AMAZE Clean sample defined in \cref{subsec:AMAZE} consistent with the $z\sim0$ relation. \\

@@

After including data from the KDS isolated field sample, the stellar mass Tully-Fisher relation defined for $V_{C}/\sigma_{int} > 1$ star-forming galaxies appears to show no evolution between $z\sim0.1$ and $z\sim3.5$.
However as we will show in \cref{subsec:rdf_v_over_sigma} the $V_{C}/\sigma_{int} > 1$ subsamples become increasingly less representative of typical star-forming galaxies with increasing redshift.

@@

In the right panel of Figure \ref{fig:tf_relation} we plot the fractional error weighted mean, median and distributions of $V_{C}$ values reported in the comparison (see \cref{app:comparison_samples}) and KDS isolated field samples to highlight two observations:
\begin{itemize}
    \item At each redshift slice the $V_{C}$ distributions are extremely broad, with mean values determined by the stellar mass of each survey.
    \item The mean isolated field sample $V_{C}$ value is less than reported in the comparison samples with similar mean $M_{\star}$ values.
    This is a result of averaging over a sample containing a higher fraction of dispersion dominated galaxies.
\end{itemize}

@@

The KDS mean and median $V_{C}$ values are $76.7^{+4.9}_{-4.5}kms^{-1}$ and $57.0^{+6.6}_{-6.3}kms^{-1}$, both of which are below the $\left<V_{C}\right> = 125kms^{-1}$ limit.
The observation of a low mean $V_{C}$ value in the full isolated field sample is primarily explainable through averaging over a sample with a higher fraction of dispersion dominated galaxies with lower rotation velocities.
This is seen in the left panel of Figure \ref{fig:tf_relation} where the dispersion dominated galaxies sit clearly below and separated from the stellar mass Tully-Fisher relation.
However it has also been discussed that pressure support, provided by turbulence and measured through the galaxy velocity dispersions, may partially compensate the gravitational force within galaxy disks and contributes to lowering the rotation velocities through an `asymmetric drift' correction \citep[e.g.][]{Burkert2010,Newman2013,Genzel2017}.
This topic is discussed further throughout \cref{sec:discussion}.

We proceed to consider the cause of the high number of dispersion dominated galaxies in our sample and the obvious candidate is the increase of velocity dispersion with redshift \citep[e.g.][]{Genzel2006,Genzel2008,ForsterSchreiber2009,Law2009,Gnerucci2011,Epinat2012,Wisnioski2015}.
There are also some galaxies in our sample where the observed velocity field has obvious rotational structure and clearly reaches flattening (e.g. see \cref{fig:dispersion_dominated_galaxies} lbg\_24 with $log(M_{\star}[M_{\odot}])=9.75$), with inferred $V_{C}$ smaller than $\sigma_{int}$.
This suggests again that the increase in random motions could influence the rotational velocities and that the accumulation of a massive stellar population is necessary to stabilise a galaxy \citep[e.g.][]{Law2009,Law2012b,Law2012c,Newman2013,Wisnioski2015}.
These ideas are explored in the following sections.

@@

In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation dominated classes, along with the AMAZE Clean sample galaxies in the $\sigma_{int}$ vs. $M_{\star}$ plane.
This is an interesting relationship to explore as it has been suggested that rotational velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
However the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret. \\

@@

In \cite{Wisnioski2015} the authors present a scaling relation describing the increase of $\sigma_{int}$ with redshift in terms of the key observable properties $f_{gas}$, $t_{depl}$ and sSFR.
Using observed constraints for these properties from \cite{Tacconi2013} leads to $\sigma_{int}$ predictions that match the data remarkably well (see \cite{Wisnioski2015} figures 10 and 11).
The relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.  \\

The mean KDS datapoint is in agreement with the scaling relation, plotted with the grey lines for $V_{C} = 125kms^{-1}$ and $log(M_{\star}[M_{\odot}])=10.0,10.3,10.6$ (note we have not shifted the datapoints to conform with a single $M_{\star}$ value as per \cite{Wisnioski2015}).
The lower $M_{\star}$ tracks suggest a flatter evolution of $\sigma_{int}$ with redshift, and indeed the surveys with lower average $M_{\star}$ (MASSIV, DYNAMO, LAW 2009, KROSS, AMAZE) have higher $\sigma_{int}$ than the surveys with larger average $M_{\star}$ (GHASP, KMOS$^{3D}$, SINS), although the exact values are sensitive to the choice of $Q_{crit}$ (shown to be $\sim1$ for the gas-rich disks observed at high-z e.g. \citealt{ForsterSchreiber2006,Genzel2011,Newman2013}) and $V_{C}$ in the equation shown in the top right of the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} (see \cref{sec:discussion}).
The tracks plotted in Figure \ref{fig:sigma_and_v_sigma_w_redshift} suggest the shape of the $\sigma_{int}$ evolution in galaxies of a particular stellar mass in the context of the equilibrium model, with these new results from the KDS providing strong observational constraints on the internal dynamics of main sequence galaxies between $z=3-3.7$.
